Joe Biden Predicted to Win 56.59% of the Popular Vote in the 2024 U.S. Presidential Election

### 2024-03-17 paper/paper.qmd
final edits!

We used R [@citeR], and the `tidyverse` [@citetidyverse], `janitor` [@citejanitor], `ggplot` [@citeggplot] packages to clean our survey and post-stratification data sets, fit our model, apply our model, and create our data visualizations.

@@

## How we produced our popular vote and electoral college predictions {#sec-first-point}

>>>>

We used R [@citeR], and the `tidyverse` [@citetidyverse], `janitor` [@citejanitor], `ggplot` [@citeggplot], `rstanarm` [@citerstanarm], and `arrow` [@citearrow] packages throughout our analtsis to clean our survey and post-stratification data sets, fit our model, apply our model, and create our data visualizations.

@@
